---
title: "p8105_hw5_hc3451"
author: "Huanyu Chen"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
library(purrr)
library(broom)
library(tibble)
library(tidyverse)
library(ggplot2)
set.seed(1)
```

# Problem 1
## (1) Baltimore
```{r}
homicide = read.csv("./homicide-data.csv")
```
The raw data contains 52179 observations of 12 variables.

```{r}
homicide = homicide |>
  mutate(city_state = paste0(city,', ',state))

homicide_summary = homicide |>
  group_by(city_state) |>
  summarise(
    total_homicides = n(),
    unsolved_homicides = sum(disposition %in% c("Closed without arrest", "Open/No arrest"))
  )
homicide_summary
```

```{r}
baltimore = homicide_summary |>
  filter(city_state == "Baltimore, MD")
prop_balti = prop.test(pull(baltimore,unsolved_homicides), pull(baltimore,total_homicides),
          alternative = "two.sided",
          conf.level = 0.95, correct = TRUE) 
save(prop_balti, file = "results/unsolved_homicides_proportion.RData")
prop_tidy = broom::tidy(prop_balti)

tidy_frame = data.frame(
  city = 'Baltimore, MD',
  estimate_prop = round(as.numeric(pull(prop_tidy, estimate[1])), 3),
  confidence_interval = paste0("(", round(pull(prop_tidy, conf.low), 3),
                               ",", round(pull(prop_tidy, conf.high), 3), ")")
  )
print(tidy_frame)
```

## (2) Each City
```{r}
prop_city = function(city) {
  homi_city = homicide_summary |>
    filter(city_state == city)
  
  prop_city = prop.test(pull(homi_city, unsolved_homicides), pull(homi_city, total_homicides),
                   alternative = "two.sided",
                   conf.level = 0.95, correct = TRUE)
  prop_city_tidy = broom::tidy(prop_city)
  
  lower_ci = round(pull(prop_city_tidy, conf.low), 3)
  upper_ci = round(pull(prop_city_tidy, conf.high), 3)
  return(data.frame(estimate_prop = round(as.numeric(pull(prop_city_tidy, estimate[1])), 3),
                    lower_ci = lower_ci,
                    upper_ci = upper_ci,
                    confidence_interval = paste0("(", lower_ci, ",", upper_ci, ")"))
  )
}

all_cities = data.frame(city_state = unique(pull(homicide_summary, city_state)))
result_df = all_cities |>
  mutate(result = map(city_state, prop_city)) |>
  unnest(result) |>
  select(city_state, estimate_prop, confidence_interval)
print(result_df)
```

## (3) Graph
```{r}
all_cities |>
  mutate(result = map(city_state, prop_city)) |>
  unnest(result) |>
  ggplot(aes(x = reorder(city_state, estimate_prop))) +
  geom_point(aes(y = estimate_prop)) +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci)) +
  labs(x = "Estimated Proportion (with 95% CI)", y = "City",
       title = "Estimated Proportion for Each City") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

# Problem 2
## (1) Combine Files
```{r, message=FALSE}
combined_data = tibble(
    files = list.files("data/"),
    path = str_c("data/", files)
    ) |>
  mutate(data = map(path, read_csv)) |>
  unnest()
```

## (2) Tidy Data
```{r}
tidy_data = combined_data |>
  mutate(files = str_replace(files, ".csv", ""),
         Group = str_sub(files, 1, 3),
         ID = str_sub(files, 5, 7)) |>
  pivot_longer(week_1:week_8,
               names_to = "Week",
               values_to = "Observations",
               names_prefix = "week_") |>
  mutate(Week = as.numeric(Week)) |>
  select(Group, ID, Week, Observations)
tidy_data
```

## (3) Graph
```{r}
tidy_data |>
  ggplot(aes(x = Week, y = Observations, color = ID)) +
  geom_line() +
  geom_point() + 
  facet_grid(~Group) +
  labs(x = 'Week', y = 'Observation', title = 'Spaghetti Plot')
```

We found that the observed values were higher in the experimental group than in the control group and tended to increase over time.

# Problem 3
## (1) mu = 0

```{r}
t_test = function(n, mu = 0, sigma = 5) {
  sim_data <- tibble(
    x = rnorm(n, mean = mu, sd = sigma)
    )
  t_test_results <- broom::tidy(t.test(sim_data))
  
  t_test_results |> 
    select(estimate, p.value)
}

sim_t_result <- tibble(
  sample_size = 30,
  iter = 1:5000
) |>
  mutate(estimate_t_test = map(sample_size, t_test)) |>
  unnest(estimate_t_test)
```

## (2) mu = 1,2,3,4,5,6
```{r}
t_test = function(mu, sigma = 5) {
  sim_data <- tibble(
    x = rnorm(30, mean = mu, sd = sigma)
    )
  t_test_results <- broom::tidy(t.test(sim_data))
  
  t_test_results |> 
    select(estimate, p.value)
}

sim_t_result_1 =
  expand_grid(
    mu_values = c(1, 2, 3, 4, 5, 6),
    iter = 1:5000
  ) |> 
  mutate(estimate_t_test = map(mu_values, t_test)) |>
  unnest(estimate_t_test) |>
  group_by(mu_values) |>
  summarise(estimate = mean(estimate), power = mean(p.value< 0.05))
```

## (3) Graph
```{r}
ggplot(sim_t_result_1, aes(x = mu_values, y = power)) +
  geom_line() +
  labs(x = "True Value of Mean", y = "Power of the Test") +
  ggtitle("Power of the Test vs. True Value of Mean")
```

```{r}
ggplot(sim_t_result_1, aes(x = mu_values, y = estimate)) +
  geom_line() +
  labs(x = "True Value of Mean", y = "Average Estimate of Mean") +
  ggtitle("Average Estimate of Mean vs. True Value of Mean")
```

```{r}
sim_t_result_2 = 
  expand_grid(
    mu_values = c(1, 2, 3, 4, 5, 6),
    iter = 1:5000
  ) |> 
  mutate(estimate_t_test = map(mu_values, t_test)) |>
  unnest(estimate_t_test) |>
  group_by(mu_values) |>
  filter(p.value > 0.05) |>
  summarise(estimate = mean(estimate))

ggplot(sim_t_result_2, aes(x = mu_values, y = estimate)) +
  geom_line() +
  labs(x = "True Value of Mean", y = "Average Estimate of Mean (when null was rejected)") +
  ggtitle("Average Estimate of Mean (when null was rejected) vs. True Value of Mean")
```

The sample average of mean across tests for which the null is rejected is not approximately equal to the true value of mean. By this way, the null will be rejected under the confidence interval.
